Effects of PCSK9 Inhibition With Evolocumab on Lipoprotein Metabolism in subjects with elevated Lp(a)

### 2019-10-07 manuscript.Rmd
Modified abstract

Background: 
Epidemiological studies show that subjects with elevated lipoprotein(a) [Lp(a)] have a higher risk for developing cardiovascular diseases. 
Inhibition of proprotein convertase subtilisin/kexin type 9 (PCSK9) is one of the limited options to reduce Lp(a). 
In this study, we aimed to investigate the effects of PCSK9 inhibition with evolocumab on lipoprotein metabolism in subjects with elevated Lp(a).

Methods:
We performed metabolic profiling of plasma samples derived from 30 individuals (placebo N = 14; evolocumab N = 16). 
By applying Bayesian lognormal regression, we assessed the effects of evolocumab treatment on circulating Lp(a) as well as 14 lipoprotein subclasses. 
Our further regression analysis revealed the distribution of LDL particles with and without apolipoprotein(a) [apo(a)] before and after evolocumab treatment.

Results:
We identified that evolocumab treatment for 16 weeks resulted in 18.9% reduction of circulating Lp(a), coupled with substantial reduction of VLDL, IDL and LDL particles. 
Moreover, we identified that evolocumab treatment not only reduced LDL particle concentrations, but also the distributions between LDL particles with and without apo(a).

Conclusions:
Based on our analysis, we suggest that the LDL particles with and without apo(a) tail may have different affinity for binding to the LDL receptor. 
Evolocumab-induced reduction of LDL particles may mainly correspond to the reduction of LDL particles without apo(a).

>>>>

Background: 
Epidemiological studies show that subjects with elevated lipoprotein(a) [Lp(a)] have a higher risk for developing cardiovascular diseases. 
Inhibition of proprotein convertase subtilisin/kexin type 9 (PCSK9) is one of the limited options to reduce Lp(a). 
In this study, we aimed to investigate metabolic effects of PCSK9 inhibition with evolocumab in subjects with elevated Lp(a).

Methods:
We performed metabolic profiling of plasma samples derived from 30 individuals (placebo N = 14; evolocumab N = 16). 
By applying Bayesian lognormal regression, we assessed the effects of evolocumab treatment on circulating metabolites such as lipoproteins and amino acids. 
Further hierarchical modeling, we also studied effects of evolocumab treatment on proportions of LDL particles with and without apolipoprotein(a) [apo(a)].

Results:
We identified that evolocumab treatment for 16 weeks resulted in 18.9% reduction of circulating Lp(a), coupled with substantial reduction of VLDL, IDL and LDL particles. 
Moreover, we observed that evolocumab treatment tended to increase the proportion of LDL particles with apo(a).

Conclusions:
Based on our analysis, we showed that evolocumab treatment had large effects on lipoprotein metabolism.
